### 2023-10-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
added a few more words to caption

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. Then, color represents the spread of the tangential
  velocity relative to the mean tangential velocity, where the average
  is taken over the region $x \in [4,10]$. 
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. Then, color represents the spread of the tangential
  velocity relative to the average tangential velocity, where the average
  is taken over the region $x \in [4,10]$. We characterize the stiff
  single-component and multicomponent vesicles as tank treading since
  the spread in the tangential velocity is below \%15, while the floppy
  single-component vesicle is not tank treading.
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}
